A preliminary constraint grammar for Russian

### 2015-03-30 2015-nodalida-ruscg/ruscg.tex
stuff
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@59577 72bbbca6-d526-0410-a7d9-f06f51895060

\author{Francis M. Tyers \\
  HSL-fakultehta, \\
  UiT Norgga árktalaš universitehta, \\
  N-9018 Romsa \\
  {\tt francis.tyers@uit.no} \\\And
  Robert Reynolds \\
  HSL-fakultehta, \\
  UiT Norgga árktalaš universitehta, \\
  N-9018 Romsa \\
  {\tt robert.reynolds@uit.no} \\}

% \author{Author1 \\
%   Affiliation / Address line 1 \\
%   Affiliation / Address line 2 \\
%   Affiliation / Address line 3 \\
%   {\tt email@domain.com} \\\And
%   Author2 \\
%   Affiliation / Address line 1 \\
%   Affiliation / Address line 2 \\
%   Affiliation / Address line 3 \\
%   {\tt email@domain.com} \\}
% 
\date{2015}

@@

Table \ref{table:ambiguity} shows the proportional prevalence of each kind of 
ambiguity. Note that these proportions do not sum to 1, since a given token may 
exhibit more than one kind of ambiguity. The first column shows the proportion 
of all tokens in a corpus that have each kind of ambiguity. The second column 
shows what proportion of ambiguous tokens exhibit each kind of ambiguity.

@@

Note that the percentages in Table~\ref{table:ambiguity} overlap, i.e. the readings of a given wordform
can have more than one kind of ambiguity. For example, the wordform \emph{zamkov} has the readings given in \ref{ex:zamkov}.

The ambiguity between \ref{ex:zamkovA} and \ref{ex:zamkovB} is morphosyntactically congruent, and
the ambiguity between \ref{ex:zamkovA}/\ref{ex:zamkovB} and \ref{ex:zamkovC} is
morphosyntactically incongruent, so this wordform would be counted for both categories in
Table~\ref{table:ambiguity} above.

@@

The morphological transducer used in this study is described in Author (2015). 
It is primarily based on Zaliznjak's \emph{Grammatical dictionary of Russian}, 
including the 2001 version's appendix of proper nouns. It also includes approximately CITE Grishina and Lyashevskaya 2008. \url{http://dict.ruslang.ru/gram.php} .

Example~\ref{ex:FSToutput} gives some examples of the output.

>>>>

%\author{Francis M. Tyers \\
%  HSL-fakultehta, \\
%  UiT Norgga árktalaš universitehta, \\
%  N-9018 Romsa \\
%  {\tt francis.tyers@uit.no} \\\And
%  Robert Reynolds \\
%  HSL-fakultehta, \\
%  UiT Norgga árktalaš universitehta, \\
%  N-9018 Romsa \\
%  {\tt robert.reynolds@uit.no} \\}

 \author{Author1 \\
   Affiliation / Address line 1 \\
   Affiliation / Address line 2 \\
   Affiliation / Address line 3 \\
   {\tt email@domain.com} \\\And
   Author2 \\
   Affiliation / Address line 1 \\
   Affiliation / Address line 2 \\
   Affiliation / Address line 3 \\
   {\tt email@domain.com} \\}

\date{2015}

@@

Table \ref{table:ambiguity} shows the proportional prevalence of each kind of 
ambiguity. The first column shows the proportion 
of all tokens in a corpus that have each kind of ambiguity. The second column 
shows what proportion of ambiguous tokens exhibit each kind of ambiguity.
Note that these proportions do not sum to 100\%, since a given token may 
exhibit more than one kind of ambiguity. For example, the wordform 
\emph{zamkov} has the readings given in \ref{ex:zamkov}.

The ambiguity between \ref{ex:zamkovA} and \ref{ex:zamkovB} is morphosyntactically congruent, and
the ambiguity between \ref{ex:zamkovA}/\ref{ex:zamkovB} and \ref{ex:zamkovC} is
morphosyntactically incongruent, so this wordform would be counted for both categories in
Table~\ref{table:ambiguity}.

@@

@@

The morphological transducer used in this study is described in Author (2015). 
It is primarily based on Zaliznjak's \emph{Grammatical dictionary of Russian}, 
including the 2001 version's appendix of proper nouns. It also includes neologisms
from Grishina and Lyashevskaya's \emph{Grammatical dictionary of new Russian words},
which is intended to be a supplement to Zaliznjak's dictionary.\footnote{\url{http://dict.ruslang.ru/gram.php}}

Example~\ref{ex:FSToutput} gives some examples of the FST's output.
